Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-06-25 manuscript/phylogenetic_signal_manuscript.tex
beginning to address DBS comments
double-checked family-wise results in main text

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. Although calculating 
  the exact type II error requires a specific alternative hypothesis, the 
  uniform distribution of p-values we obtained after permuting the permuted 
  networks means that the type II error would increase linearly as the 
  alternative hypothesis was set farther from zero.
  % [[Is this cogent? Correct? If not, I think I will have to remove all reference to type II error and hope we don't get the same reviewer again. It may not be an issue since we've moved away from the motif-like measures.]]
  % DBS: I think it's fine.

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    For the 47 families % DBS: Alyssa, please check this number!
    that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    % DBS: According to the table, this should probably be Apiaceae and Poaceae. Please check.
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

    % DBS: The section above seems like it would fit better in the Methods and then we just say nothing about these families.

@@

  \begin{table}[!h]
  \caption{
  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rr|| l rr|}
    \hline
    Family  & Change in log odds & $P$-value & Family  & Change in log odds & $P$-value \\
    \hline
    \emph{Adoxaceae}  & -65.8 &  0.163  &     \emph{Melastomataceae}*   & 5.19  &  0.577 \\
    \emph{Amaryllidaceae}   & -17.9 &  \textbf{0.015} &     \emph{Montiaceae}   & -1.12 &  0.870 \\
    \emph{Apiaceae}   & 10.9  &  \textbf{0.006} &     \emph{Myrtaceae}  & 8.55  &  0.071 \\
    \emph{Apocynaceae}  & -6.96 &  \textbf{0.037} &     \emph{Oleaceae}   & 0.995 &  0.855 \\
    \emph{Asparagaceae}   & -6.23 &  0.189  &     \emph{Onagraceae}   & -556  &  \textgreater0.999 \\
    \emph{Asteraceae}*  & -1.47 &  \textbf{\textless0.001}  &     \emph{Orchidaceae}  & -14.5 &  0.145 \\
    \emph{Berberidaceae}  &   -1.48$\times10^3$   &  \textgreater0.999  &     \emph{Orobanchaceae}  & 24.2  &  0.326 \\
    \emph{Boraginaceae}   & -5.15 &  \textbf{\textless0.001}  &     \emph{Papaveraceae}   & -11.2 &  0.511 \\
    \emph{Brassicaceae}   & -11.2 &  0.072  &     \emph{Phyllanthaceae}   & 9.99  &  0.433 \\
    \emph{Calceolariaceae}  & 156 &  0.998  &     \emph{Plantaginaceae}   & -8.48 &  \textbf{0.001} \\
    \emph{Campanulaceae}  & 334 &  0.999  &     \emph{Poaceae}*   & 69.2  &  \textbf{0.003} \\
    \emph{Caprifoliaceae}   & 0.31  &  0.959  &     \emph{Polygonaceae}   & -14.8 &  \textbf{\textless0.001} \\
    \emph{Caryophyllaceae}  & 2.09  &  0.644  &     \emph{Primulaceae}  & 14.9  &  0.343 \\
    \emph{Cistaceae}  & -11.4 &  \textbf{\textless0.001}  &     \emph{Ranunculaceae}  & -38 &  \textbf{\textless0.001} \\
    \emph{Convolvulaceae}   & -1.84 &  0.837  &     \emph{Rosaceae}   & 0.759 &  0.735 \\
    \emph{Ericaceae}  & 4.61  &  0.116  &     \emph{Rubiaceae}*   & -13 &  \textbf{0.026} \\
    \emph{Fabaceae}*  & -12.9 &  \textbf{\textless0.001}  &     \emph{Salicaceae}   & -1.9  &  0.545 \\
    \emph{Geraniaceae}  & -3.31 &  0.624  &     \emph{Sapindaceae}  & 821 &  0.999 \\
    \emph{Hydrangeaceae}  & 0.057 &  0.982  &     \emph{Saxifragaceae}  & -0.092  &  0.992 \\
    \emph{Iridaceae}  & -27.9 &  0.078  &     \emph{Solanaceae}   & -21.9 &  0.189 \\
    \emph{Lamiaceae}  & -5.01 &  \textbf{\textless0.001}  &     \emph{Tropaeolaceae}  & 192 &  0.997 \\
    \emph{Loasaceae}  & -865  &  \textgreater0.999  &     \emph{Verbenaceae}  & -9.03 &  0.627 \\
    \emph{Malpighiaceae}  & 2.8 &  0.168  &     \emph{Violaceae}  & -0.487  &  0.974 \\
    \emph{Malvaceae}  & -5.56 &  0.363  &   &   & \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
    \end{center}
     \caption{Change in log odds of observing pairwise niche overlap per million
     years of divergence time between a pair of plants
     in the 14 plant families where there was a significant
     relationship between log odds of sharing interaction
     partners and phylogenetic distance.
     % DBS: The above is near indecipherable. Can we please simplify it substantially?
     Families in pollination networks are indicated
     by dark purple diamonds while families in herbivory
     networks are indicated by pale green circles.
     Note that changes in log odds are analogous to the 
     slopes of the regression lines from Eq. 2-3
     in logit-transformed space and represent
     the change in the probability of observing shared 
     interaction partners per million years of divergence time. We also
     show the slope of the relationship between the
     log-odds of observing each overlap pattern and 
     phylogenetic distance across all plant families
     in herbivory (pale, green horizontal line) and
     pollination (dark, purple horizontal line) networks.
     % See~\emph{Figure S1; Supporting Information} for more details.
     The phylogenetic tree below the plots indicates the
     relatedness between these plant families. Error bars represent 95\% confidence
     intervals.}
    \label{within_family_regression}
  \end{figure}

>>>>

    This permutation approach also allows us to estimate type I and type II 
    error for our analysis. To do this, we created 500 permutations of each 
    permuted network and, again keeping the observed phylogenetic distances 
    between plant species, repeated our analyses. We can then determine the 
    number of permuted networks which appear to have significant 
    overlap-phylogenetic distance relationships relative to the permutations 
    of these permuted networks (type I error). Type II error can be determined
    from the distribution of p-values obtained when comparing the permuted 
    networks to permutations of the permuted networks. Although calculating 
    the exact type II error requires a specific alternative hypothesis, the 
    uniform distribution of p-values we obtained after permuting the permuted 
    networks means that the type II error would increase linearly as the 
    alternative hypothesis was set farther from zero.

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    For the 48 families that were well represented in pollination networks, overlap decreased
    with increasing phylogenetic distance in 18 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 15 plant families. Finally, the overlap between pairs of \emph{Polygonaceae}
    % DBS: According to the table, this should probably be Apiaceae and Poaceae. Please check.
    increased with increasing phylogenetic distance. 
    Of the seven plant families that were sufficiently well represented in herbivory 
    networks, overlap decreased with increasing phylogenetic distance in four 
    (Table~\ref{family_slopes_ph}; Fig.~\ref{within_family_regression}). Two
    families did not show significant relationships between phylogenetic distance and overlap,
    and in one family, \emph{Fabaceae}, overlap of interaction partners increased with 
    increasing phylogenetic distance.

@@

  \begin{table}[!h]
  \caption{
  \small Change in log odds (per million years of phylogenetic distance) of a pair of plants in the same family sharing a pollinator.}
  % These are from the regressions within each family. P-vals need to be replaced, to come from randomizations. Coefficients should be fine.
  \small
  \label{family_slopes_pp}
  \begin{tabular}{|l  rr|| l rr|}
    \hline
    Family  & Change in log odds & $P$-value & Family  & Change in log odds & $P$-value \\
    \hline
    \emph{Adoxaceae}  & -65.8 & 0.163 & \emph{Malvaceae}  & -5.56 & 0.363 \\
    \emph{Amaryllidaceae} & -17.9 & \textbf{0.015}  & \emph{Melastomataceae}* & 5.19  & 0.577 \\
    \emph{Apiaceae} & 10.9  & \textbf{0.006}  & \emph{Montiaceae} & -1.12 & 0.87  \\
    \emph{Apocynaceae}  & -6.96 & \textbf{0.037}  & \emph{Myrtaceae}  & 8.55  & 0.071 \\
    \emph{Asparagaceae} & -6.23 & 0.189 & \emph{Oleaceae} & 0.995 & 0.855 \\
    \emph{Asteraceae}*  & -1.47 & \textbf{\textless0.001} & \emph{Onagraceae} & -556  & \textgreater0.999 \\
    \emph{Berberidaceae}  & -1.48$\times10^3$ & \textgreater0.999 & \emph{Orchidaceae}  & -14.5 & 0.145 \\
    \emph{Boraginaceae} & -5.15 & \textbf{\textless0.001} & \emph{Orobanchaceae}  & 24.2  & 0.326 \\
    \emph{Brassicaceae} & -11.2 & 0.072 & \emph{Papaveraceae} & -11.2 & 0.511 \\
    \emph{Calceolariaceae}  & 156 & 0.998 & \emph{Phyllanthaceae} & 9.99  & 0.433 \\
    \emph{Campanulaceae}  & 334 & 0.999 & \emph{Plantaginaceae} & -8.48 & \textbf{0.001}  \\
    \emph{Caprifoliaceae} & 0.31  & 0.959 & \emph{Poaceae}* & 69.2  & \textbf{0.003}  \\
    \emph{Caryophyllaceae}  & 2.09  & 0.644 & \emph{Polygonaceae} & -14.8 & \textbf{\textless0.001} \\
    \emph{Cistaceae}  & -11.4 & \textbf{\textless0.001} & \emph{Primulaceae}  & 14.9  & 0.343 \\
    \emph{Convolvulaceae} & -1.84 & 0.837 & \emph{Ranunculaceae}  & -38 & \textbf{\textless0.001} \\
    \emph{Ericaceae}  & 4.61  & 0.116 & \emph{Rosaceae} & 0.759 & 0.735 \\
    \emph{Fabaceae}*  & -12.9 & \textbf{\textless0.001} & \emph{Rubiaceae}* & -13 & \textbf{0.026}  \\
    \emph{Geraniaceae}  & -3.31 & 0.624 & \emph{Salicaceae} & -1.9  & 0.545 \\
    \emph{Hydrangeaceae}  & 0.057 & 0.982 & \emph{Sapindaceae}  & 821 & 0.999 \\
    \emph{Iridaceae}  & -27.9 & 0.078 & \emph{Saxifragaceae}  & -0.092  & 0.992 \\
    \emph{Lamiaceae}  & -5.01 & \textbf{\textless0.001} & \emph{Solanaceae} & -21.9 & 0.189 \\
    \emph{Lauraceae}  & -79.9 & \textbf{\textless0.001} & \emph{Tropaeolaceae}  & 192 & 0.997 \\
    \emph{Loasaceae}  & -865  & \textgreater0.999 & \emph{Verbenaceae}  & -9.03 & 0.627 \\
    \emph{Malpighiaceae}  & 2.8 & 0.168 & \emph{Violaceae}  & -0.487  & 0.974 \\
  \hline
  \end{tabular}
  \smallskip
  \footnotesize

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
    \end{center}
     \caption{Change in log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases. For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type.       Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} and \emph{Poaceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types. All other plant families were well-represented in only one network type.
     % DBS: The above is near indecipherable. Can we please simplify it substantially?
     [[Simpler now?]]
     Families in pollination networks are indicated
     by dark purple diamonds while families in herbivory
     networks are indicated by pale green circles.
     Note that changes in log odds are analogous to the 
     slopes of the regression lines from Eq. 2-3
     in logit-transformed space and represent
     the change in the probability of observing shared 
     interaction partners per million years of divergence time. We also
     show the slope of the relationship between the
     log-odds of observing each overlap pattern and 
     phylogenetic distance across all plant families
     in herbivory (pale, green horizontal line) and
     pollination (dark, purple horizontal line) networks.
     % See~\emph{Figure S1; Supporting Information} for more details.
     The phylogenetic tree below the plots indicates the
     relatedness between these plant families. Error bars represent 95\% confidence
     intervals.}
    \label{within_family_regression}
  \end{figure}

### 2019-06-25 manuscript/supporting_info.tex
double-checked family-wise results in main text

>>>>

\section*{Supporting information 3: Details of within-family regressions}

    Models for nine families could not be fit because there was no variation in the phylogenetic distance between plants, their numbers of shared interaction partners, or both. These families were \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Cactaceae}, \emph{Cornaceae}, \emph{Gentianaceae}, \emph{Liliaceae}, \emph{Oxalidaceae}, \emph{Rhamnaceae}, and \emph{Zingiberaceae}. Further, we could not fit a model for \emph{Sapindaceae} in herbivory networks as all but one plant pair had the same phylogenetic distances.

    Only five families were sufficiently well-represented to fit models for shared herbivores: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}. All were also well-represented enough to fit models for shared pollinators.

    In total, there were 48 families which were well-represented enough to fit models for shared pollinators. For 13 of these, we obtained singular fits.
    Singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
    \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
    \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
    \emph{Saxifragaceae}, \emph{Verbenaceae}.

    6+42=48
    \emph{Sapindaceae}
